Efficiently summarising relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-09-06 treestats_paper.tex
flag unclear reference to method

We do not know the true genealogies underlying real data,
but recent methods are available to estimate them.
To evaluate the correspondence between site and branch statistics
in real data,
we calculated mean sequence diversity along chromosome 20 from the 1000 Genomes dataset
in 1Mb windows separately in each of the five continental groupings,
calculated using the site statistic described in Example~\ref{ex:site_diversity},
and compared this to the corresponding branch statistic (of Example~\ref{ex:branch_diversity})
as calculated from three inferred tree sequences:
by tsinfer \citep{tsinfer}, which does not attenpt to estimate well-calibrated node times,
(2) by GEVA \citep{geva}, which aims to calibrate the node times reported by tsinfer,
and (3) by Relate \citep{relate}, an independently developed method.
All calculations were done only using the portions of the chromosome
passing the ``strict'' mask for sequencing accessibility.
Separate curves for each of the 26 populations are shown in Supplemental Figure \ref{fig:chr20_full}.

>>>>

We do not know the true genealogies underlying real data,
but recent methods are available to estimate them.
To evaluate the correspondence between site and branch statistics
in real data,
we calculated mean sequence diversity along chromosome 20 from the 1000 Genomes dataset
in 1Mb windows separately in each of the five continental groupings,
calculated using the site statistic described in Example~\ref{ex:site_diversity},
and compared this to the corresponding branch statistic (of Example~\ref{ex:branch_diversity})
as calculated from three inferred tree sequences:
by tsinfer \citep{tsinfer}, which does not attenpt to estimate well-calibrated node times,
(2) by GEVA \citep{geva}, which aims to calibrate the node times reported by tsinfer,
and (3) by Relate \citep{relate}, an independently developed method.
All calculations were done only using the portions of the chromosome
\krt{unclear what this means--ref/citation is needed.}
passing the ``strict'' mask for sequencing accessibility.
Separate curves for each of the 26 populations are shown in Supplemental Figure \ref{fig:chr20_full}.
